Convex Surrogates via Polyhedral Losses

### 2019-04-02 jessie-writeup/jessie-notes.tex
Added ranking example

	\item Do we want to test this construction for ranking on 3 outcomes?

@@

>>>>

	\item Do we want to test this construction for ranking on 3 outcomes?  (See below)

@@

\section{Ranking example}
Let us consider the ranking property on $3$ outcomes.
The simplex can be drawn as follows:

\begin{figure}
\begin{center}
\begin{tikzpicture}[scale=4.0]

 \draw[thick] (0, 1/ sqrt 2) --  (-1/2, 0) 
 -- (1/2, 0) -- (0,1/ sqrt 2) ;

 \draw[fill = blue, opacity=0.2] (0, 0.375 / sqrt 2) --  (-1/2, 0) 
  -- (0, 0) -- (0, 0.375 / sqrt 2) ;
 \draw[fill = green, opacity=0.2] (0, 0.375 / sqrt 2) --  (1/2, 0) 
  -- (0, 0) -- (0, 0.375 / sqrt 2) ;
 \draw[fill = red, opacity=0.2] (0, 0.375 / sqrt 2) --  (0,1/sqrt 2) 
    -- (1/4, 0.5/sqrt 2) -- (0, 0.375 / sqrt 2) ;
 \draw[fill = purple, opacity=0.2] (0, 0.375 / sqrt 2) --  (0, 1/sqrt 2) 
      -- (-1/4, 0.5/sqrt 2) -- (0, 0.375 / sqrt 2) ;
 \draw[fill = yellow, opacity=0.2] (0, 0.375 / sqrt 2) --  (-1/4, 0.5/sqrt 2) 
        -- (-1/2, 0) -- (0, 0.375 / sqrt 2) ;
 \draw[fill = orange, opacity=0.2] (0, 0.375 / sqrt 2) --  (1/4, 0.5/sqrt 2) 
          -- (1/2, 0) -- (0, 0.375 / sqrt 2) ;

  \node at (-0.6,0) {$y_1$};
  \node at (0,1.2 / sqrt 2) {$y_2$};
  \node at (0.6,0) {$y_3$};
  \node at (-0.2,.2) {*};
  %\fill (0, 0.375 / sqrt 2) circle[radius=1pt];

\end{tikzpicture}
\caption{The ranking property for $n=3$.}
\label{fig:ranking-simplex}
\end{center}
\end{figure}

We know from our paper that it is $n-1=2$-embeddble from our paper, and the characterization of Ramaswamy et al. shows us this is tight.
However, if we want to apply our construction to construct a loss eliciting the ranking over three outcomes, consider the following $H$-rep construction.

I started by choosing $B^*$ corresponding to the cell with the $*$ in it.
In this cell, we know $p_1 \geq p_2 \geq p_3$ here, and so we can start by representing $B^*$ with the matrix

\[
B^* = \begin{bmatrix*}
1 & -1 & 0 \\
0 & 1 & -1 \\
0 & 0 & 1
\end{bmatrix*}
\]

Knowing that I needed to choose (at least) 3 normals, I chose $V$ somewhat intuitively to form a triangle and then tinkered with it until the normals worked.
With these normals, we can actually use the same set of normals for each cell, as in the abstain example.
Consider 
\[
V = \begin{bmatrix*}
-1/2 & -1/2 \\
0 & 1  \\
1/2 & -1/2 
\end{bmatrix*}
\]

The polytopes then appear as follows (and are similar for each cell.)
The large triangle that the polytopes are all inside is $V^\circ$.
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{./ranking}
\caption{Polytopes $T(*, y)$ for each $y \in \Y$.}
\label{fig:ranking}
\end{figure}
